---
title: "WSG Upstream Feedback Summary"
author: ""
date: "2023-02-22"
output:
  html_document: default
  word_document: default
  pdf_document: default
---


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Prelims
library(qualtRics)
library(here)
library(sjlabelled)
library(dplyr)
library(knitr)
library(kableExtra)
library(stringr)
library(ggplot2)
library(ggrepel)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Pull in Data

#Include Priors y/n (survey filled out by the research team to describe partial information given by advisory team members that did not respond to the survey)?
Priors <- "y"


#load qualtrics Survey Data & Analysis -> export -> select "use numeric values"
CulvSurvey <- read_survey(here("Upstream UX Survey_February 22, 2023_11.33.csv"))

if (Priors == "y") {
  
  CulvSurvey
  
} else {
  
   CulvSurvey <-  CulvSurvey %>% filter(!str_detect(Q1, "Prior"))
  
}
  

#load effort and comments
CulvEffort <- read.csv(here("comments_mockup_summary.xlsx - Summary_2_15_23.csv"))
adtlcomments <- read.csv(here("comments_mockup_summary.xlsx - AddtlFeatures_2_15_23.csv"))
```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Effort by Question Number
lables <- as.data.frame(get_label(CulvSurvey)) #make df from question number and description (with id)

EffortbyQ <- as.data.frame(rownames(lables)) %>% #make description a var and combine
                      rename("Question"= "rownames(lables)" )%>%
                      cbind(lables)%>%
                      mutate(id = str_sub(`get_label(CulvSurvey)`,start = -4, end= -2))%>% #Pull question id
                      mutate(id = ifelse(id == " 06", "g06",id))%>% #hot fix for labeling error (06->g06)%>%
                      left_join(CulvEffort, by = "id") #join PI effort scores
                      
```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Analyze Importance (1 - 3)

#Summarize Importance Scale (Average)
Avg_Importance <- CulvSurvey %>%
                select(contains("#1"))%>% #select only importance questions (labeled #1)
                na_if(4)%>% # questions coded 4 means "I don't understand), so make NA
                summarise_all(funs(mean(., na.rm = TRUE)))%>% #take average
                t()

#Include Effort
Importance_Effort <- as.data.frame(rownames(Avg_Importance)) %>% #extract descriptions as variables
                rename("Question" = "rownames(Avg_Importance)") %>%
                cbind(Avg_Importance)%>%
                left_join(EffortbyQ, by = "Question")%>%
                mutate(Difficulty = as.factor(Difficulty))

#Plot
Importance_Plot <- ggplot(Importance_Effort, aes(x = Difficulty, y = Avg_Importance, label=id)) +
                     geom_point(aes(color = Difficulty))+
                     geom_text_repel(aes(label = id,  color = Difficulty), size = 4)+
                     scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
                     theme_classic()




```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Analyze Top 5


#Summarize Scale (Count)
Top5 <- CulvSurvey %>%
                select(contains("#2"))%>%  
                summarise_all(funs(sum(!is.na(.))))%>% # Count Non-NA as a vote for top 5
                t()
#Include Difficulty
Top5_Effort <- as.data.frame(rownames(Top5)) %>% #extract descriptions as variables
                rename("Question" = "rownames(Top5)") %>%
                cbind(Top5)%>%
                left_join(EffortbyQ, by = "Question")%>%
                mutate(Difficulty = as.factor(Difficulty))

#Plot
Top5_Plot <- ggplot(Top5_Effort, aes(x = Difficulty, y = Top5, label=id)) +
                     geom_point(aes(color = Difficulty))+
                     geom_text_repel(aes(label = id,  color = Difficulty), size = 4)+
                     scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
                     theme_classic()

```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Tables

Importance_Table <- Importance_Effort %>%
                    left_join(select(Top5_Effort,Top5,id), by = "id")%>%
                    mutate(Difficulty = as.numeric(Difficulty))%>%
                    select(id, "Feature" = Proposed.Feaure, 
                           "Avg Importance" = Avg_Importance, 
                           Top5, Difficulty, 
                           "Top Choice" = TopChoice,  
                           Comments)%>%
                    arrange(desc(Avg_Importance), desc(Top5),Difficulty)%>%
                      kbl()%>%
                      kable_paper(full_width = F)%>%
                      footnote( "Ordered by Average Importance, vote for Top 5, then Difficulty.")

                      #column_spec(3, color = "white", background = spec_color(Avg_Importance, option= "C", end = 0.3, direction = -1))%>%
                      #column_spec(4, color = "white", background = spec_color(Top5, option= "C", end = 0.3, direction = -1))
              
adtlcomments <-adtlcomments %>%
              kbl()%>%
              kable_paper(full_width = F)%>%
              footnote("From meeting comments and online survey")

```


This report summarizes data collected through in-meeting comments and a UX survey provided to seven advisory committee members on 2/15/2023 following a demo of the Upstream app.

### Feature Rankings
The following table ranks average feature importance, whether it was considered a top 5 priority, along with if and who chose it as a top 1 priority. Difficulty of implementing each feature was also ranked by the PI team. Among participants, four surveys were returned + 1 "prior" survey that was filled out by the PI team to incorporate additional information discussed by members who did not complete a survey.

```{r echo=FALSE, message=FALSE, warning=FALSE}
Importance_Table
```

### Additional Features
Below are advisory committee members suggestions for other features they would see useful, but were not mentioned in the meeting/survey:
```{r echo=FALSE, message=FALSE, warning=FALSE}
adtlcomments
```

### Plots
The following figures plot average importance and top 5 inclusion by PI ranked difficulty to implement. Feature numbers can be cross referenced to the first table in this report.
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
Importance_Plot
```

<br>
```{r echo=FALSE, message=FALSE, warning=FALSE}
Top5_Plot
```



